---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# The BiclustGUI for R Commander

`RcmdrPlugin.BiclustGUI` is a R Commander Plug-In containing multiple methods to apply biclustering and visualise these results.

## Installing the GUI

To install the **CRAN Release Version** (1.0.6), please use the following commands:

```{r, eval=FALSE,echo=TRUE}
setRepositories(ind=c(1:5))
install.packages("RcmdrPlugin.BiclustGUI")
```

To install the **Development Version** (1.0.7) from either the *R-Forge* or *GitHub* repository use

```{r, eval=FALSE,echo=TRUE}
setRepositories(ind=c(1:5))
install.packages("RcmdrPlugin.BiclustGUI",repos="http://R-Forge.R-project.org")
```
or
```{r, eval=FALSE,echo=TRUE}
setRepositories(ind=c(1:5))
install.packages("devtools") # If not yet installed on your R Version
devtools::install_github("hadley/devtools") # Only run this if your currently installed 
                                            # devtools version is <= 1.12 (recursive dependencies bug)

devtools::install_github("ewouddt/RcmdrPlugin.BiclustGUI")
```

One of the options above will install the GUI and its dependencies from both CRAN and Bioconductor. Should some issue arise with a package installation, please try to manual install them. The code for this can be found [here](https://ibiostat.be/online-resources/online-resources/biclustgui/biclustgui).

On the initial start-up of R Commander, you will probably be prompted to install some additional dependencies. This should not take too long!

To launch the GUI, use:
```{r, eval=FALSE,echo=TRUE}
library(RcmdrPlugin.BiclustGUI)
```

## More Info & Links

* *Introductory Blog on GitHub/R-Bloggers* (See [Blogpost](https://ewouddt.github.io/RcmdrPlugin.BiclustGUI/2016/09/27/biclustGUI/)).
* *Detailed Guide* (See [Vignette](https://github.com/ewouddt/RcmdrPlugin.BiclustGUI/raw/master/vignettes/GuideBiclustGUI.pdf)).
* *Shiny Application for Biclustering* ([Shiny Cloud](https://uhasselt.shinyapps.io/shiny-biclust/) + [Stand-Alone](https://ibiostat.be/online-resources/online-resources/biclustgui/shinyapp) + GitHub (Coming Soon))
* *R-Forge Project Page* ([R-Forge](https://r-forge.r-project.org/R/?group_id=2104)).
* *I-Biostat Page* ([I-Biostat](https://ibiostat.be/online-resources/online-resources/biclustgui/biclustgui)).


## Currently Available Methods/Diagnostics

| R Package  | Biclustering Method | Publication |
|----------|----------------------------|----------------|
| `biclust` | Plaid | Turnet *et al.*, 2005 |
| `biclust` | $\delta$-biclustering | Cheng and Church, 2000 |
| `biclust` | X Motif | Murali and Kasif, 2003 |
| `biclust` | Spectral | Kluger *et al.*, 2003 |
| `biclust` | QuestMotif | Kaiser, 2011 |
| `biclust` | Bimax | Prelic *et al*., 2006 |
| `fabia` | FABIA | Hochreiter *et al.*, 2010 |
| `isa2` | The Iterative Signature Algorithm | Bergman *et al*., 2003 |
| `iBBiG` | Iterative Binary BIclustering of Genesets | Gusenleitner *et al*., 2012 |
| `rqubic` | Qualitative Biclustering | Li *et al*., 2009 |
| `BicARE` | Biclustering Analysis and Results Exploration | Gestraud and Barillot, 2014 |
| `s4vd` | SSVD (Sparse Singular Value Decomposition) | Lee *et al*., 2010 |
| `s4vd` | S4VD (SSVD incorporating stability correction) | Sill *et al*., 2011 |
|**R Package**|**Diagnostics**|**Publication**|
| `BcDiag` | Bicluster Diagnostic Plots | Aregay *et al*., 2014 |
| `superbiclust` | Generating Robust Biclusters from a Bicluster Set | Khamiakova, 2013 |

Table: All included biclustering and diagnostics packages in the BiclustGUI:


